---
title: "Network Selection"
output: html_notebook
---

**we registered three main questions**

**1** - Homophily- Do participants choose people who are closer to their rating

**2** - Friending vs. Unfriending - is there a difference in homophily when looking at the manipulation

**3** - Choice strategyf

**4** - stickiness.



```{r , echo=FALSE,include=FALSE}
rm(list = ls())

library (Rmisc);library(tidyverse);library(lme4); library (lmerTest);library(tidyboot)

#upload all the csv files into one data set 
d =
    list.files(pattern="*.csv")  %>% # create a list of all csv files in the folder  
    map_df(~read_csv(.))

#d = subset (d, subject_id!=c(49)) #,68,78
#ask how man unique particpiants we have
#length(unique(d$subject_id))

#create a difference score between the individual rating and each other chosen participant-this is used later in the simularion??
d$difKeep1 = d$kept_1_rating-d$subject_rating
d$difKeep2 = d$kept_2_rating-d$subject_rating
d$difKeep3 = d$kept_3_rating-d$subject_rating
d$difElim1 = d$elim_1_rating-d$subject_rating
d$difElim2 = d$elim_2_rating-d$subject_rating
d$difElim3 = d$elim_3_rating-d$subject_rating

d$condition = factor (d$condition, label = c("select", "control") )

#average keep columns 
d$realKeepMean= rowMeans(d[,c('kept_1_rating', 'kept_2_rating', 'kept_3_rating')], na.rm=T)

d$difKeepMean = rowMeans(d[,c('difKeep1', 'difKeep1', 'difKeep1')], na.rm=T)



#*****add sentistrength data**************
#Create a dataset that matach the sentiment analysis file
sent = d%>%
 select(condition,subject_id, trial, ends_with("rating"), ends_with("title"), -starts_with("kept"), -starts_with("elim") )%>%
 gather(agent, value, -subject_id, -trial,-condition)%>%
 separate(agent, into = c("agent","question"), sep ="\\_")%>%
 spread(question, value)%>%
 select(subject_id,trial,agent)

#download sentiment file
t = read_csv("C:/Users/chaga/Google Drive/research/network selection/network_regulation_study_1_police_brutality/data/data_emotion_sentiment/allText_out.csv")
t=cbind(sent,t) #bind file


#resturcture the sentiment file in a way that could be added to d
t= t%>%
 unite(agent1,sentPos,sentNeg,Text, sep ="%" )%>%
 spread(agent, agent1)%>%
 separate(a1, into = c("a1_sentPos", "a1_sentNeg","Text"), sep ="\\%")%>%
 separate(a2, into = c("a2_sentPos", "a2_sentNeg","Text"), sep ="\\%")%>%
 separate(a3, into = c("a3_sentPos", "a3_sentNeg","Text"), sep ="\\%")%>%
 separate(a4, into = c("a4_sentPos", "a4_sentNeg","Text"), sep ="\\%")%>%
 separate(a5, into = c("a5_sentPos", "a5_sentNeg","Text"), sep ="\\%")%>%
 separate(a6, into = c("a6_sentPos", "a6_sentNeg","Text"), sep ="\\%")%>%
separate(subject, into = c("subject_sentPos", "subject_sentNeg","Text"), sep ="\\%")%>%
select(-Text)

d =left_join(d, t, by = c("subject_id","trial")) # add to d

rm(t, sent)
  

 
#average keep columns 
#d$realKeepMean= rowMeans(d[,c('kept_1_rating', 'kept_2_rating', 'kept_3_rating')], na.rm=T)
#d$difKeepMean = rowMeans(d[,c('difKeep1', 'difKeep1', 'difKeep1')], na.rm=T)


#**********add moderators to file*************************
#m = read_csv('./moderators/network_moderators.csv') # we are reading the moderators file (which was collected via qualtrics)
#m = m[,c(19:93)] #cleaning
#m$idenScale = rowMeans(m[,c('iden1', 'iden2', 'iden3', 'iden4','iden5')], na.rm=T)
#m$idenScale = m$idenScale-13

#m=m%>%
#  select (subject_id,poli,idenScale)

#d = left_join(d,m, by="subject_id")
#rm(m)

#d$iden2=ifelse (d$idenScale<3.2,1,2)
#d$poli2=ifelse (d$idenScale<3,1,2)


#long format of peer ratings and difference
dl = d %>% 
  gather(keepNumber, peerRating,kept_1_rating,kept_2_rating,
         kept_3_rating,elim_1_rating,
         elim_2_rating,elim_3_rating)%>%
  separate(keepNumber, into = c("elimKeep", "number", "qq"), sep ="\\_")%>%
  select(subject_id, trial,condition,subject_rating,elimKeep, number, peerRating)

dl$elimKeep=factor(dl$elimKeep,label = c("eliminated","kept"))
dl$number=as.integer(dl$number)

dl$peerDif=  dl$peerRating-dl$subject_rating 

rm(peerLong)


#a table with averate rating of each participant - this is added to later graphs.
rating = d %>%
  group_by(subject_id)%>%
  summarise(
    ratingMean = mean(subject_rating) # get mean rating for each participant
    #condition = first(condition) #get the condition they were assigned to
    ) 

d =left_join(d, rating, by = "subject_id")


#subsets 
s = subset (d, condition == "select")
sl = subset (dl, condition == "select")
c = subset (d, condition == "control")
cl = subset (dl, condition == "control")

rm(rating)


#con = dl%>% #creating a dateframe con based d 
#  group_by(subject_id) %>%
#  select(subject_id, condition)%>%
#  slice (1)

#write.csv(con, "conditionId.csv")

```


```{r descriptieves}

des = d%>%
  group_by(id)%>%
  select(age)
```


###1 - Values kept

Let's first look at kept ratings for the control and the selection condition and see if they are difference

```{r}

r= lmer(peerRating~condition +(1|subject_id), dl); summary(r)


dfc <- summarySE(dl, measurevar="peerRating", groupvars=c("condition","elimKeep"), na.rm = T)

#dfc$elimKeep=factor(dfc$elimKeep, label = c("eliminate", "keep"))
pd <- position_dodge(0)
ggplot(dfc, aes(x=condition, y=peerRating, fill=elimKeep)) + 
    geom_bar(position=position_dodge(), stat="identity", colour="black" ) +
    labs(title="")+
    guides(fill=guide_legend(title=NULL))+
    theme_bw()+
    theme(plot.title = element_text(size = rel(1.5)),
          axis.title.y = element_text(face="bold",  size=14),
          axis.text.x  = element_text( vjust=0.5, size=18),
          axis.text.y  = element_text( vjust=0.5, size=12),
          axis.title.x = element_blank()) +  
  coord_cartesian(ylim=c(3, 6)) +
  ylab("Peer Rating")+
  geom_errorbar(aes(ymin=peerRating-ci, ymax=peerRating+ci),
                  width=.1,position=position_dodge(.9))



```

kept participants over time 
```{r}

r = lmer(peerRating~scale(trial)*condition +(1|subject_id),dl);summary(r)


dfc <- summarySE(dl, measurevar="peerRating", groupvars=c("elimKeep", "trial","condition"), na.rm = T)

dfc=subset(dfc, elimKeep== "kept")

g = (ggplot(dfc,aes(x=trial, y=peerRating ,fill = condition))
  + geom_errorbar(aes(ymin=peerRating-se, ymax=peerRating+se), width=.1) 
  + geom_line( aes(linetype= condition, group=condition),size = 1.2) 
  +geom_point() 
  #+scale_y_continuous(limits = c(3, 7))
  +theme_bw()
  +theme(legend.title=element_blank(),
         #legend.position =  "none",
         axis.title.y = element_text(  size=14),
         axis.text.x  = element_text( vjust=0.5, size=14),
         axis.text.y  = element_text( vjust=0.5, size=12),
         axis.title.x = element_text(vjust=0.5, size=14)) 
  +labs(title = "Kept participants as a function of trial number", x = "Trial number", y = "Ratings"));g



dfc <- summarySE(dl, measurevar="peerRating", groupvars=c("elimKeep", "trial","condition"), na.rm = T)

dfc = subset (dfc, elimKeep =="kept")

g = (ggplot(dfc,aes(x=trial, y=peerRating ,fill = condition, colour = condition))
  +stat_smooth(aes(linetype=condition, colour =condition), 
              size =1.2, method='lm',fill = "grey", 
              se = T, na.rm =T) 
  +theme_bw()
  +theme(legend.title=element_blank(),axis.title.y = element_text(  size=14),axis.text.x  = element_text( vjust=0.5, size=14),axis.text.y  = element_text( vjust=0.5, size=12),axis.title.x = element_text(vjust=0.5, size=14))
  +labs(title = "keep as a function of trial number", x = "Trial number", y = " Keep"));g

```


###2 - homophily

I am using the the difference between participants and the users that each participants kept vs. eliminated. 

```{r homophily}
#look at the absolute value compare elim v keep
#r = lmer (difValue~ elimKeep+(1|subject_id), sl) ; summary (r)


dfc <- summarySE(dl, measurevar="peerDif", groupvars=c("elimKeep","condition"), na.rm = T)

pd <- position_dodge(0)
ggplot(dfc, aes(x=condition, y=peerDif, fill=elimKeep)) + 
    geom_bar(position=position_dodge(), stat="identity", colour="black" ) +
    labs(title=" Difference between kept users and the participant")+
    guides(fill=guide_legend(title=NULL))+
    theme_bw()+
    theme(plot.title = element_text(size = rel(1.5)),
          axis.title.y = element_text(face="bold",  size=14),
          axis.text.x  = element_text( vjust=0.5, size=18),
          axis.text.y  = element_text( vjust=0.5, size=12),
          axis.title.x = element_blank()) +  
  coord_cartesian(ylim=c(-1.5, 1)) +
  ylab("Difference")+
  geom_errorbar(aes(ymin=peerDif-ci, ymax=peerDif+ci),
                  width=.1,position=position_dodge(.9))



```



``` {r homophily over time,include=FALSE}

#r = lmer (abs(peerDif)~ elimKeep*trial+(1|subject_id), sl) ; summary (r)


dfc <- summarySE(dl, measurevar="peerDif", groupvars=c("elimKeep", "trial","condition"), na.rm = T)

dfc=subset(dfc, elimKeep=="kept")

g = (ggplot(dfc,aes(x=trial, y=peerDif ,fill = condition,colour = condition))
  #+ geom_errorbar(aes(ymin=peerDif-ci, ymax=peerDif+ci), width=.1) 
  +stat_smooth(aes(linetype=condition, colour =condition), 
              size =1.2, method='lm',fill = "grey", 
              se = T, na.rm =T) 
  #+geom_point() 
 # +scale_y_continuous(limits = c(-1, 3.5))
  +theme_bw()
  +theme(legend.title=element_blank(),
         axis.title.y = element_text(  size=14),
         axis.text.x  = element_text( vjust=0.5, size=14),
         axis.text.y  = element_text( vjust=0.5, size=12),
         axis.title.x = element_text(vjust=0.5, size=14)) 
  +labs(title = "Difference to keep as a function of trial number", x = "trial number", y = " difference"));g


g = (ggplot(dfc,aes(x=trial, y=peerDif ,fill = condition))
  + geom_errorbar(aes(ymin=peerDif-ci, ymax=peerDif+ci), width=.1) 
  + geom_line( aes(linetype= condition, group=condition),size = 1.2) 
  +geom_point() 
  +scale_y_continuous(limits = c(-2.5, 2))
  +theme_bw()
  +theme(legend.title=element_blank(),
         legend.position =  "none",
         axis.title.y = element_text(  size=14),
         axis.text.x  = element_text( vjust=0.5, size=14),
         axis.text.y  = element_text( vjust=0.5, size=12),
         axis.title.x = element_text(vjust=0.5, size=14)) 
  +labs(title = "Select condition: difference to kept participants as a function of trial number", x = "trial number", y = "Difference"));g

```



There is a significant difference between the people participants choose to keep and the people particiapnts choose to eliminate.


##2 - difference in rating bewteen the conditions 

```{r difference in condition, echo=FALSE}
r = lmer(subject_rating~ condition + (trial|subject_id),dl);summary(r)

r = lmer(subject_rating~ condition *trial + (trial|subject_id),dl);summary(r)


#graph
dfc <- summarySE(dl, measurevar="subject_rating", groupvars=c("elimKeep", "condition"), na.rm = T)

dfc=subset(dfc,elimKeep=="kept")

dfc$ci = c(.23,.23)

ggplot(dfc, aes(x=condition, y=subject_rating, fill=condition)) + 
    geom_bar(position=position_dodge(), stat="identity", colour="black" ) +
    labs(title="")+
    guides(fill=guide_legend(title=NULL))+
    theme_bw()+
    theme(plot.title = element_text(hjust=0.5,size = rel(1.5)),
          axis.title.y = element_text(face="bold",  size=14),
          axis.text.x  = element_text( vjust=0.5, size=18),
          axis.text.y  = element_text( vjust=0.5, size=12),
          axis.title.x = element_blank(),
          legend.position="none") +   
  coord_cartesian(ylim=c(4.5, 6)) +
  #facet_wrap(~elimKeep)+
  labs(title= "Participants' Ratings" , y= "ratings")+
  geom_errorbar(aes(ymin=subject_rating-ci, ymax=subject_rating+ci),
                  width=.1,position=position_dodge(.9))

```

```{r rating over time,echo=FALSE}

r = lmer(subject_rating~ trial*condition + (1|subject_id),d);summary(r)

dfc <- summarySE(dl, measurevar="subject_rating", groupvars=c("condition", "trial"), na.rm = T)

g = (ggplot(dfc,aes(x=trial, y=subject_rating ,fill = condition,colour=condition))
  + geom_point(shape =1)
  #+ geom_errorbar(aes(ymin=subject_rating-ci, ymax=subject_rating+ci), width=.1) 
  +stat_smooth(aes(linetype=condition, colour =condition), 
              size =1.2, method='lm',fill = "grey", 
              se = T, na.rm =T) 
  #+geom_point() 
  #+scale_y_continuous(limits = c(3.5, 6))
  +theme_bw()
  +theme(plot.title = element_text(hjust = 0.5, size = rel(1.5) ),
        legend.title=element_blank(),
         axis.title.y = element_text(  size=14),
         axis.text.x  = element_text( vjust=0.5, size=14),
         axis.text.y  = element_text( vjust=0.5, size=12),
         axis.title.x = element_text(vjust=0.5, size=14))
  +labs(title = "Emotions per Trial Number", x = "Trial", y = "Emotion Ratings"));g

```

the goal of this analysis is to examine whether participants whose bias is bi

```{r correlation - bias and rating}

dlc = subset (dl, elimKeep=="kept"& condition =="select")
dlc=dlc %>%select(-condition, -elimKeep,-peerDif)

dlc =dlc %>%
  gather (rater, valueRating,-subject_id, -trial, -number)


r = lmer(valueRating~ rater +(1|subject_id),dlc);summary(r)

#get a slope per participant
model_bias= dlc%>%
  group_by(subject_id)  %>% 
  do(r = lm(valueRating~ rater , data = .))%>%
  mutate(bias = r$coefficients[[2]])%>%
  select(-r)

    #models is the lms for all participants

model_rating = sl%>%
  group_by(subject_id)%>%
  do(r = lm(subject_rating~ trial , data = .))%>%
  mutate(ratingChange = r$coefficients[[2]])%>%
  select(-r)

model = left_join(model_bias,model_rating, by = "subject_id")

cor.test(model$ratingChange,model$bias)



ggplot(model, aes(x=ratingChange, y=bias)) +
    geom_point(shape=1) +    
    geom_smooth()

```


###3 - comparing to various algorithms - see Vibha's code  

We look at the users that participants kept: 

1. What would happen if you compared it to a random selection.
2. What would happen if you just took the 3 people closest to you. 
3. What would happen if you just sampled the most liberal group. 


```{r keep compare values,echo=FALSE}
#get the true count keep

# add a simulation of an average of 1000 random choices. 
s <- s %>% 
  rowwise() %>% # this basically instruct r to loop by row 
  mutate( #
    randKeepMean = list(c(a1_rating, a2_rating, a3_rating, a4_rating, a5_rating, a6_rating)), #create a list of these columns 
    randKeepMean = list(sample(randKeepMean, 3, replace = F)), # create a list of 1000 o samples
    randKeepMean  = mean (randKeepMean) #average them 
    )

#Creat the average of the homophily
dHom= s %>% 
  gather(a1_rating,a2_rating, a3_rating, a4_rating,a5_rating,a6_rating, key = otherRating, value = rating)  %>% # turn these columns to long format
  group_by(subject_id, trial) %>% #group by trial and subject_id
  mutate(abs_rank = abs(rating - subject_rating)) %>% #for each one take the absolute value of the difference between the ratings and the subject own ratings
  arrange(subject_id,trial,abs_rank) %>% # arragne them according to size
  slice(1:3)%>%
  summarize (meanKeptHom = mean(rating))


#changed this code to choose one sided homophily
dLib= s %>% 
  gather(a1_rating,a2_rating, a3_rating, a4_rating,a5_rating,a6_rating, key = otherRating, value = rating)  %>% # turn these columns to long format
  group_by(subject_id, trial) %>% #group by trial and subject_id
  mutate(libRank = ifelse(rating - subject_rating<0,10,rating - subject_rating))%>% #for each one take the absolute value of the difference between the ratings and the subject own ratings
  arrange(subject_id,trial,libRank) %>% # arragne them according to size
  slice(1:3)%>%
  summarize (meanKeptLib = mean(rating))


s = left_join(s,dHom, by = c("subject_id", "trial"))
s = left_join(s,dLib, by= c("subject_id", "trial"))

median(s$ratingMean)
s$lowHigh =ifelse (s$ratingMean<=5,1,2)



dStrategyCompare=s %>%
  gather(randKeepMean,meanKeptHom,realKeepMean,meanKeptLib, key=keepType, value= value ) 


r =lmer(value~keepType+(1|subject_id),dStrategyCompare);summary(r)
#confint(r,level =.95)

dfc <- summarySE(dStrategyCompare, measurevar="value", groupvars=c("keepType"), na.rm = T)

dfc$keepType=factor(dfc$keepType, labels=c("Max Homophily","One Sided Homophily", "Random chooser", "Actual choice"))

dfc = subset(dfc, keepType!= "Random chooser")
#dfc$value[3]=5.39
keepType=c("Max Homophily","One Sided Homophily","Actual choice")
pd <- position_dodge(0)

#dfc$ci = c(0.19,0.18)

#dfc = subset (dfc , keepType != "Random chooser")


g=ggplot(dfc, aes(x=keepType, y=value, fill=keepType)) + 
    scale_x_discrete(limits=keepType)+
    geom_bar(position=position_dodge(), stat="identity", colour="black" ) +
    labs(title="")+
    guides(fill=guide_legend(title=NULL))+
    theme_bw()+
    theme(plot.title = element_text(hjust = 0.5,size = rel(1.5)),
          axis.title.y = element_text(face="bold",  size=14),
          axis.text.x  = element_text( vjust=0.5, size=16),
          axis.text.y  = element_text( vjust=0.5, size=12),
          axis.title.x = element_blank(),legend.position="none") +  
    coord_cartesian(ylim=c(4.5, 6)) +
  scale_fill_manual(values=c("#99CCFF", "#FF9999", "#000000"))+
  #facet_wrap(~ poli)+
  labs(title= "Average Ratings of Kept Participants", y= "Kept rating")+
  geom_errorbar(aes(ymin=value-ci, ymax=value+ci),
                  width=.1,position=position_dodge(.9));g



g=ggplot(dfc, aes(x=keepType, y=value, fill=keepType)) + 
    scale_x_discrete(limits=keepType)+
    geom_bar(position=position_dodge(), stat="identity", colour="black" ) +
    labs(title="")+
    guides(fill=guide_legend(title=NULL))+
    theme_bw()+
    theme(plot.background = element_rect(fill = "black"),
        panel.background = element_rect(fill = 'black'),
        #panel.border = element_blank(),
        panel.grid = element_blank(),
        legend.background= element_rect(fill="black", colour=NA),
        legend.text = element_text(colour = 'white'),
        plot.title = element_text(size = rel(1.3),hjust =.5, colour = 'white'),
        axis.title.y = element_text(face="bold",  size=14,colour = "white"),
        axis.text.x  = element_text( vjust=0.5, size=14,colour = "white"),
        axis.text.y  = element_text( vjust=0.5, size=16,colour = "white"),
        axis.title.x = element_blank()) +  
    coord_cartesian(ylim=c(4.5, 6)) +
  scale_fill_manual(values=c("#99CCFF", "#FF9999", "#66cc60"))+
  #facet_wrap(~ poli)+
  labs(title= "Average Ratings of Kept Participants", y= "Kept rating")+
  geom_errorbar(aes(ymin=value-ci, ymax=value+ci),
                  width=.1,position=position_dodge(.9), colour= 'white');g

#rm(dHom, dLib,dStrategyCompare,)

```




###4 - stickiness of users

```{r stickiness - setup}
#add a map function insted of creating three codes
stickCounter = function (df, keptVar, id=quo(subject_id), trial = quo(trial)){
  keptVar = enquo(keptVar)
  df %>%
    select(!!id, !!trial,!!keptVar)%>% #select a few variable 
    mutate(id =!!keptVar, 
           id_above= lag(!!keptVar),#variable and the one above
           id_below= lead(!!keptVar)) %>% #variable and the one below
    mutate(compare_above=(id==id_above),
           kept=(id==id_below)) %>%   #compare these - true false.
    replace_na(list(compare_above = 0))  %>%   # convert to 01
    replace_na(list(kept = 0))  %>%   # convert to 01
    group_by(subject_id,!!keptVar) %>% 
    mutate(sticky = cumsum(compare_above))%>%
    ungroup()%>%
    select(subject_id, trial, sticky, kept)
}


a1=stickCounter(d,a1_id)
a2=stickCounter(d,a2_id)
a3=stickCounter(d,a3_id)
a4=stickCounter(d,a4_id)
a5=stickCounter(d,a5_id)
a6=stickCounter(d,a6_id)

colnames(a1)= c("subject_id","trial","a1_sticky","a1_decisionKeep")
colnames(a2)= c("subject_id","trial","a2_sticky","a2_decisionKeep")
colnames(a3)= c("subject_id","trial","a3_sticky","a3_decisionKeep")
colnames(a4)= c("subject_id","trial","a4_sticky","a4_decisionKeep")
colnames(a5)= c("subject_id","trial","a5_sticky","a5_decisionKeep")
colnames(a6)= c("subject_id","trial","a6_sticky","a6_decisionKeep")

d= left_join(d,a1,by=c("subject_id","trial")); rm(a1)
d= left_join(d,a2,by=c("subject_id","trial")); rm(a2)
d= left_join(d,a3,by=c("subject_id","trial")); rm(a3)
d= left_join(d,a4,by=c("subject_id","trial")); rm(a4)
d= left_join(d,a5,by=c("subject_id","trial")); rm(a5)
d= left_join(d,a6,by=c("subject_id","trial")); rm(a6)


q = d%>%
  select (subject_id,trial,condition, stimulus,subject_rating,a1_rating,a2_rating,a3_rating,a4_rating,a5_rating,a6_rating, ends_with("sticky"),ends_with("decisionKeep"))%>%
  gather(question, value, -subject_id,-trial,-condition,-stimulus,-subject_rating)%>%
  separate(question, into = c("agent", "question"), sep ="\\_")%>%
  separate(agent, into = c("removeThis","agent"),sep=1)%>%
  select (-removeThis)%>%
  spread(question,value)%>%
  mutate(stickyBinary =ifelse(sticky>=1,1,0))

q$dist = q$rating-q$subject_rating

```


```{r stickiness}

mean (q$sticky)

median(x = q$sticky)


r = lmer (decisionKeep~ stickyBinary+dist+ (1|subject_id),q);summary(r)


dfc <- summarySE(q, measurevar="decisionKeep", groupvars=c("sticky"), na.rm = T)
dfc =subset(dfc,sticky<7)

g = (ggplot(dfc,aes(x=sticky, y=decisionKeep ))
  + geom_errorbar(aes(ymin=decisionKeep-ci, ymax=decisionKeep+ci), width=.1) 
  + geom_line( size = 1.2) 
  +geom_point() 
  #+scale_y_continuous(limits = c(-.5, 1.5))
  +theme_bw()
  + geom_hline(yintercept = 0.5,linetype="dashed", color = "red")
  +theme(plot.title = element_text(hjust = 0.5),
        legend.title=element_blank(),
         axis.title.y = element_text(  size=14),
         axis.text.x  = element_text( vjust=0.5, size=14),
         axis.text.y  = element_text( vjust=0.5, size=12),
         axis.title.x = element_text(vjust=0.5, size=14)) 
  +labs(title = "Probability of Being Kept Again", x = "Number of kept trials", y = "p (keep)"));g


r = lmer (decisionKeep~ stickyBinary+dist+ (1|subject_id),q);summary(r)

```

```{r}

r= glmer (decisionKeep~ stickyBinary*dist + (1|subject_id), q) ; summary (r)


dfc <- summarySE(q, measurevar="decisionKeep", groupvars=c("dist", "stickyBinary"), na.rm = T)

dfc$stickyBinary=factor(dfc$stickyBinary, label = c("new", "previously kept"))

dfc =subset(dfc,N>15)



g = (ggplot(dfc,aes(x=dist, y=decisionKeep,colour = stickyBinary ))
  #+ geom_errorbar(aes(ymin=subject_rating-ci, ymax=subject_rating+ci), width=.1) 
  +stat_smooth(aes(linetype=stickyBinary, colour =stickyBinary), 
              size =1.2, method='lm',fill = "grey", 
              se = T, na.rm =T) 
  #+geom_point() 
  #+scale_y_continuous(limits = c(3.5, 6))
  +theme_bw()
  +theme(legend.title=element_blank(),axis.title.y = element_text(  size=14),axis.text.x  = element_text( vjust=0.5, size=14),axis.text.y  = element_text( vjust=0.5, size=12),axis.title.x = element_text(vjust=0.5, size=14))
  +labs(title = "", x = "Distance from participants", y = "p (keep)"));g

```
###sentiment Analysis

```{r add sentiment analysis file- setup}
#setup for sentistrength create a txt file with all the texts. 
#sent = d%>%
#  select(condition,subject_id, trial, ends_with("rating"), ends_with("title"), -starts_with("kept"), -starts_with("elim") )%>%
#  gather(agent, value, -subject_id, -trial,-condition)%>%
#  separate(agent, into = c("agent","question"), sep ="\\_")%>%
#  spread(question, value)


#text = sent%>%
#  select (title)
#write.table(text,"allText.txt",sep="\t",row.names=FALSE, col.names = FALSE)

s = d%>%
  select(condition,subject_id, trial, ends_with("rating"), 
         ends_with("title"), -starts_with("kept"),
         -starts_with("elim"),ends_with("sentPos"), 
         ends_with("sentNeg") )%>%
  gather(agent, value, -subject_id, -trial,-condition)%>%
  separate(agent, into = c("agent","question"), sep ="\\_")%>%
  spread(question, value)

s$sentNeg =as.numeric(s$sentNeg)
s$sentPos =as.numeric(s$sentPos)
s$rating =as.numeric(s$rating)


cor.test(s$rating,s$sentPos)
cor.test(s$rating,s$sentNeg)
cor.test(s$rating,s$sentTot)




ggplot(sent, aes(x=rating, y=sentNeg)) +
    geom_point(shape=1,position=position_jitter(width=.5,height=.5)) +    
    geom_smooth(method=lm)

```

```{r difference analysis}

# I need to restructure the files in order to get this ansswer


```


###word nuber as predictor 

```{r}
wc = d %>% 
  select(subject_id,condition,stimulus,subject_rating,starts_with("kept"),starts_with("elim"))%>%
  gather(key,value, -subject_id,-condition,-stimulus, -subject_rating)%>%
  separate(key, into = c("elimKeep", "number", "question"), sep ="\\_")%>%
  spread(question, value)%>%
  mutate(wordCount = sapply(gregexpr("[[:alpha:]]+", title), function(x) sum(x > 0)))

wc$elimKeep= factor (wc$elimKeep)
wc$elimKeep = ifelse (wc$elimKeep=="elim",0,1)
wc$rating=as.integer(wc$rating)

r = glmer (elimKeep~ condition*wordCount+(1|subject_id),wc);summary(r)


wc%>%
  group_by(condition) %>%
  do(print(summary((glmer(elimKeep~ log(wordCount)+rating+(1|subject_id),family=binomial, data=.)))))


wc%>%
  group_by(condition) %>%
  do(print(summary((lmer(rating~ wordCount+(1|subject_id), data=.)))))


r = lmer (rating~ log(wordCount)+(1|subject_id),wc);summary(r)

rm (wc)
```

#### aditional analysis

```{r trial by trial prediction}


robb = d%>%
  #slice (1:10)%>%
  arrange(subject_id, trial)%>%
  select(condition,subject_id, trial, ends_with("rating"), -starts_with("a"))%>%
  mutate(meanKeptPrevious = lag((kept_1_rating+kept_2_rating+kept_3_rating)/3))%>%
  mutate(meanElimPrevious = lag((elim_1_rating+elim_2_rating+elim_3_rating)/3))%>%
  mutate(meanPrevious = (meanKeptPrevious+meanElimPrevious)/2)


r= lmer (subject_rating~meanKeptPrevious+ (1|subject_id), robb) ;summary(r)

r= lmer (subject_rating~meanElimPrevious+ (1|subject_id), robb) ;summary(r)

r= lmer (subject_rating~meanPrevious+ (1|subject_id), robb) ;summary(r)

```






```{r }
#look at the absolute value compare elim v keep
#r = lmer (peerDif~ elimKeep+(1|subject_id), sl) ; summary (r)


dfc <- summarySE(subset(dl,condition == "select" & elimKeep=="kept"), measurevar="peerDif", groupvars=c("elimKeep","subject_id"), na.rm = T)




```






```{r moderators, include=FALSE,echo=FALSE}
m = read_csv('./moderators/network_moderators.csv') # we are reading the moderators file (which was collected via qualtrics)
m = m[,c(19:93)] #cleaning
d = left_join(d,m, by="subject_id") #combining the two datasets based on participants' id

hist(d$poli)

d$libCon = ifelse(d$poli <4,1,2)











r = lmer (keepMean~closeKeep*poli+(1|subject_id),dCloser);summary(r)

dc = dCloser %>%
  group_by(poli,closeKeep)%>%
  summarise(keepMean= mean(keepMean))

dc = left_join(dc,rating , by="subject_id")

dc$difKeep = dc$ratingMean-dc$keepMean


#grpah 
ggplot()+
  geom_point(data= dc, 
             aes(x=poli, y=keepMean, color=closeKeep),
             shape=1,
             position = position_jitter(w = 0, h = .5))




```





```{r habituation, include=FALSE,echo=FALSE}


r = lmer(subject_rating~ trial +(1|subject_id), d);summary(r)
# it seems that participants are habituating. 

```
power analysis
```{r , include=FALSE,echo=FALSE}

p = subset (dl, subject_id <15)

length (unique(p$subject_id))
library (simr)

p$absdif = abs(p$peerDif)
r = lmer (absdif~ difCondition+(1|subject_id), p) ; summary (r)

p$difCondition= ifelse(p$difCondition == "difKeep", 1,2)

p$difCondition =as.integer(p$difCondition)

p$difCondition =factor(p$difCondition)
powerSim(r,fixed("difCondition"),nsim=30)

fixef(r)
```


##graphs to presentation 
 
```{r homophily1}

dfc <- summarySE(dl, measurevar="peerDif", groupvars=c("elimKeep","condition"), na.rm = T)


dfc$elimKeep=factor(dfc$elimKeep, labels = c("Eliminated", "Kept"))

#dfc$peerDif[3] = .30
pd <- position_dodge(0)
g=ggplot(dfc, aes(x=condition, y=peerDif, fill=elimKeep)) + 
  geom_bar(position='dodge', stat="identity", colour="black" ) +
  labs(title=" Difference between kept users and the participant")+
  guides(fill=guide_legend(title=NULL))+
  theme_bw()+
  theme(plot.background = element_rect(fill = "black"),
        panel.background = element_rect(fill = 'black'),
        panel.border = element_blank(),
        panel.grid = element_blank(),
        legend.background= element_rect(fill="black", colour=NA),
        legend.text = element_text(colour = 'white'),
        plot.title = element_text(size = rel(1.3),hjust =.5, colour = 'white'),
        axis.title.y = element_text(face="bold",  size=14,colour = "white"),
        axis.text.x  = element_text( vjust=0.5, size=18,colour = "white"),
        axis.text.y  = element_text( vjust=0.5, size=16,colour = "white"),
        axis.title.x = element_blank()) +  
  geom_errorbar(aes(ymin=peerDif-ci, ymax=peerDif+ci),
                  width=.1,position=position_dodge(.9),colour='white')+
  labs(title = "Peer Emotions in Relation to Participant Emotions", 
       x = "",
       y = "")+
  scale_fill_manual(values=c("#99CCFF", "#FF9999", "#000000"))+
  geom_vline(xintercept = 1.5,linetype="dashed", color = "white")+
  geom_hline(yintercept = 0,linetype= 'dashed', color = "white")+
  annotate("text", x = 1.6, y = -1.6, label = "Less Emotional",colour ='white', size = 4.5)+
  annotate("text", x = 1.6, y = 1.6, label = "More Emotional", colour = 'white', size = 4.5)+
  coord_flip(ylim=c(-2, 2));g



```


```{r ratings}

dfc <- summarySE(dl, measurevar="subject_rating", groupvars=c("condition", "trial"), na.rm = T)

g = (ggplot(dfc,aes(x=trial, y=subject_rating ,fill = condition,colour=condition))
  + geom_point(shape =1)
  #+ geom_errorbar(aes(ymin=subject_rating-ci, ymax=subject_rating+ci), width=.1) 
  +stat_smooth(aes(linetype=condition, colour =condition), 
              size =1.2, method='lm',fill = "grey", 
              se = T, na.rm =T) 
  #+geom_point() 
  +scale_y_continuous(limits = c(4.5, 6))
  +theme_bw()
  +theme(plot.background = element_rect(fill = "black"),
        panel.background = element_rect(fill = 'black'),
        #panel.border = element_blank(),
        panel.grid = element_blank(),
        legend.background= element_rect(fill="black", colour=NA),
        legend.text = element_text(colour = 'white'),
        plot.title = element_text(size = rel(1.3),hjust =.5, colour = 'white'),
        axis.title.y = element_text(face="bold",  size=14,colour = "white"),
        axis.text.x  = element_text( vjust=0.5, size=18,colour = "white"),
        axis.text.y  = element_text( vjust=0.5, size=16,colour = "white"),
        axis.title.x = element_text(face="bold",  size=14,colour = "white")) 
  +scale_fill_manual(values=c("#99CCFF", "#FF9999", "#000000"))

  +labs(title = "Participant Emotions per Trial Number", x = "Trial Number", y = "Emotion Ratings"));g

```
```{r}

s=subset(s,agent != "subject")
write.csv(s,"sentiment_value.csv")

ak = d%>%select (trial,ends_with("id"),-starts_with("elim"))

write.csv(ak, "PeerIds.csv")

```

```{r convert to json}
library(jsonlite)

table = read_csv("C:/Users/chaga/Google Drive/research/network selection/network_regulation_study_1_police_brutality/agent_ratings_FEMALE.csv")


table =toJSON(table)

write(table, 'C:/Users/chaga/Google Drive/research/network selection/js_tasks/agent_data/agent_rating_FEMALE.json')
```
#vibha simulation  - compare max homphily, one sided homophily an d

```{r prepare the data}



#upload the library
library(tidyverse)
library(tidyboot)
library(reshape2)

#get real data
realData =
    list.files(pattern="*.csv")  %>% # create a list of all csv files in the folder  
    map_df(~read_csv(.))

idList = unique(realData$subject_id)


#import simulation data
simResults = read_csv("model_simulation/simulation_results.csv")%>%
  filter(id %in% idList)

names(simResults) <- c("subject_id", "strategy", "mean_mean", "mean_ci_low", "mean_ci_high","diff_mean","diff_ci_low","diff_ci_high","loyalty_mean","loyalty_ci_low","loyalty_ci_high")




#rename real data conditions
realData$condition = factor (realData$condition, label = c("select", "control") )
#only take experimental participants
realData = subset(realData, condition == "select")

#only keep relevant columns
realData = realData %>%
  select(subject_id, subject_rating, kept_1_rating, kept_2_rating, kept_3_rating)

#find mean difference per round
#ASK: do you want absolute value of difference?
realData["difference_1"] <- realData$kept_1_rating - realData$subject_rating
realData["difference_2"] <- realData$kept_2_rating - realData$subject_rating
realData["difference_3"] <- realData$kept_3_rating - realData$subject_rating
realData["diff_mean"] <- rowMeans(realData[c('difference_1', 'difference_2', 'difference_3')])

#find mean kept score per round
#ASK: ok to do it like this, i.e. n = 20
realData["kept_mean"] <- rowMeans(realData[c('kept_1_rating', 'kept_2_rating', 'kept_3_rating')])

#use tidyboot to create an mean average kept score
realMean = realData %>%
  group_by(subject_id) %>%
  tidyboot_mean(column = kept_mean)

realMean = realMean %>%
  select(-empirical_stat, -n)

names(realMean) <- c("subject_id", "mean_ci_low", "mean_mean", "mean_ci_high")

realDiff = realData %>%
  group_by(subject_id) %>%
  tidyboot_mean(column = diff_mean)

realDiff = realDiff %>%
  select(-empirical_stat, -n)

names(realDiff) <- c("subject_id", "diff_ci_low", "diff_mean", "diff_ci_high")

realResults = left_join(realMean, realDiff, by = 'subject_id')
  

simResults=simResults%>%
  select(-starts_with("loyal"))


realResults$strategy="real"


simData = rbind(realResults,simResults)





meansSimulation =simData%>%
  group_by(strategy)%>%
  summarize (strategyMean = mean(mean_mean, na.rm =T))

```

```{r graph results}


r =lmer (mean_mean ~ strategy+ (1|subject_id),simData);summary(r)


dfc <- summarySE(simData, measurevar="mean_mean", groupvars=c("strategy"), na.rm = T)


ggplot(dfc, aes(x=strategy, y=mean_mean, fill=strategy)) + 
    geom_bar(position=position_dodge(), stat="identity", colour="black" ) +
    labs(title="")+
    guides(fill=guide_legend(title=NULL))+
    theme_bw()+
    theme(plot.title = element_text(hjust=0.5,size = rel(1.5)),
          axis.title.y = element_text(face="bold",  size=14),
          axis.text.x  = element_text( vjust=0.5, size=18),
          axis.text.y  = element_text( vjust=0.5, size=12),
          axis.title.x = element_blank(),
          legend.position="none") +   
  coord_cartesian(ylim=c(4.5, 6)) +
  #facet_wrap(~elimKeep)+
  labs(title= "mean of simulation" , y= "mean_mean")+
  geom_errorbar(aes(ymin=mean_mean-ci, ymax=mean_mean+ci),
                  width=.1,position=position_dodge(.9))




```

